---
title: "lab4"
author:
 - "Isaac Tetteh"
 - "Laurence Vander Werff"
 - "Joshua Limaye"
 - "Ruben arias"
date: "March 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
## [Link](https://github.com/isaac34mi/lab4) to github repo.

### Reading and inspecting Avengers data 
```{r}
av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)
str(av)
```
```{r}
knitr::kable(head(av))
```

### Data tidying


##### gathering on death
```{r}
deaths <- av %>% gather(key=Time, value = Death,
              c(Death1, Death2, Death3,
                Death4, Death5)) %>%
              mutate(Time = parse_number(Time, na = c("", "NA"))) %>%
              select(-c(URL,Notes))
```
#### gathering on returns
```{r}
returns <- av %>% gather(key=Time, value = Return,
                     c(Return1, Return2, Return3,
                       Return4, Return5)) %>%
                  mutate(Time = parse_number(Time, na = c("", "NA"))) %>%
                  select(-c(URL,Notes))
```

```{r}
knitr::kable(head((deaths)))      
```

```{r}
knitr::kable(head(returns))
```

### Statement Validation 

```{r}
returns %>% filter(Return == "YES") %>% dim()
```
The above code addresses the statement that "...on 57 occasions the individual made a comeback.   
By filtering on return and checking the dimensions, we can see we have 57 rows verifying the article's claim

```{r}
total_death <- deaths %>% filter(Death == "YES") %>% summarise(Total_Death = n()) 
```
We were able to verify that, there were ``r total_death`` total deaths.
